Proposed Solution

### 2017-01-25 CAV17/secs/postanal.tex
fix beginning of rule graph part

\app can output the set of learned rules from the training set as
described in $\S$\ref{sec-learn}. Recall that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is sufficient for \app to perform its core task of
configuration file validation, but can be used for more than 
simple rule checking. By interpreting the rules as a graph (which
we call the {\bf Rule Graph}), we can 
use tools from graph theory to extract information
about the configuration space. We inspect properties of this 
Rule Graph to sort reported errors by those most likely to be valid.
To demonstrate the additional value of the Rule Graph, we
also use it to estimate the complexity of configuration settings.

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
In contrast, the model output from a neural network is not as easily 
amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
to build on the work of previously developed methods and tools.
The following section provides a precise definition of the Rule Graph
and the metrics derived for the purposes of ranking reported errors
and complexity analysis.

>>>>

The learner outputs a set of rules learned from the training set as
described in Sec.~\ref{sec-learn}. Recall that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is necessary to perform the core verification task,
but can also be used for further analysis. By interpreting the rules as a graph (which
we call the {\bf Rule Graph}), we can 
use tools from graph theory to extract information
about the configuration space that can improve the quality of the learned model.
We inspect properties of this 
Rule Graph to sort reported errors by those most likely to be valid.
To demonstrate the additional value of the Rule Graph, we
also use it to estimate the complexity of a configuration file.

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
While it is possible to analyze the models from other machine learning techniques such as neural networks~\cite{lei2016rationalizing} and
conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
In contrast the Rule Graph is a relatively simple, yet information rich, representation of the learned model.
The following section provides a precise definition of the Rule Graph
and demonstrates useful metrics we derive for the purposes of ranking reported errors
and complexity analysis.
